---
title: "Gleison Medeiros"
---

```{r, include=FALSE}
library(htmltools)
library(here)
source(here("_tmp/R", "functions.R"))
```

### {{< fa circle-user >}} Bio 

:::{.bio-row}
:::{.bio-column-right}

```{r out.width='275px', out.extra='style="display:block; margin-left:auto; margin-right:auto; clip-path: circle();"'}
#| echo: false
knitr::include_graphics("https://avatars.githubusercontent.com/u/71445184?v=4")
```
:::

:::{.bio-column-left}
Masters student in Bioinformatics at the Federal University of Rio Grande do Norte (UFRN) and a graduate in Biomedicine from the same institution. My academic journey is focused on omics data analysis, with an emphasis on Single Cell, RNA-seq, Metagenomics, and the Evolution of Biological Systems. Since 2021, I have been part of the BioME team, where I apply computational approaches to investigate evolutionary patterns and protein interaction networks, contributing to a deeper understanding of molecular complexity and large-scale biological mechanisms.

:::
:::

:::{.column-body style="margin-top:-20px;"}
```{r}
#| echo: false

tags$div(class = "row", style = "display: flex;",
         
create_button(
  icon = "fab fa-github fa-xl",
  url = "https://github.com/gleisonm"
),
create_button(
  icon = "fas fa-globe fa-xl",
  url = "http://lattes.cnpq.br/3943323611794371"

),
create_button(
  icon = "fab fa-linkedin-in fa-xl",
  url = "https://www.linkedin.com/in/gleison-azevedo-504380353/"
)
)
```
:::


