---
title: "Isaac Medeiros"
---

```{r, include=FALSE}
library(htmltools)
library(here)
source(here("_tmp/R", "functions.R"))
```

### {{< fa circle-user >}} Bio 

:::{.bio-row}
:::{.bio-column-right}

```{r out.width='275px', out.extra='style="display:block; margin-left:auto; margin-right:auto; clip-path: circle();"'}
#| echo: false
knitr::include_graphics("https://avatars.githubusercontent.com/u/127994907?v=4")
```
:::

:::{.bio-column-left}
Undergraduate student in Information Technology, with a degree in Ecology from the Federal University of Rio Grande do Norte. I aim to develop skills with an emphasis on Software Engineering, focusing on creating technological tools that help mitigate societal challenges. In this way, I incorporate the practices and experiences from my Bachelor's in Ecology to convey a message with a social and environmental perspective.

:::
:::

:::{.column-body style="margin-top:-20px;"}
```{r}
#| echo: false

tags$div(class = "row", style = "display: flex;",
         
create_button(
  icon = "fab fa-github fa-xl",
  url = "https://github.com/MedeirosIsaac"
),
create_button(
  icon = "fas fa-globe fa-xl",
  url = "http://lattes.cnpq.br/8138760654810810/"
)
)
```
:::


